Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-14 manuscript/manuscript.Rmd
RL discussion update

For our use case, the environment will be a computational model of the population dynamics of a fishery, with the environment state at time $t$ being a vector of all the fish populations, $N_t=(X_t,Y_t,Z_t)$.
At each time step, the agent observes the state $S$ and harvests $X$,
\begin{align*}
  (X_t, Y_t, Z_t) \mapsto ((1-M_X)\cdot X_t, Y_t, Z_t),
\end{align*}
where the fish mortality-from-harvest $M_X=M_X(N_t)$ is the agent's action at time $t$. 
This secures a reward of $M_X(N_t)X$.
Afterwards, the environment undergoes a time step under its natural dynamics given by \eqref{eq:3d model stoch}.

>>>>

For our use case, the environment will be a computational model of the population dynamics of a fishery, with the environment state at time $t$ being a vector of all the fish populations, e.g. $N_t=(X_t,Y_t,Z_t)$ in the three species case.
At each time step, the agent observes the state $S$ and enacts some harvest---reducing $X_t$ to $X_t - M_X(N_t)\cdot X_t$, and, in the two-fishery scenario, also reducing $Y_t$ to $Y_t - M_Y(N_t)\cdot Y_t$.
Here the fish mortality-rates-from-harvest (i.e. $M_X=M_X(N_t)$ and $M_Y=M_Y(N_t)$), are the agent's action at time $t$. 
This secures a reward of $M_X(N_t)X$ in the single fishery case, and in the two-fishery case the reward is $M_X(N_t)X + M_Y(N_t)Y$.
After this harvest portion of the time step, the environment changes according to its natural dynamics given by \eqref{eq:3d model stoch}.

As mentioned, this discretized time framework allows a simplification of the possibly seasonal mating behavioral patterns of the species involved. 
This approximation is commonly used in fisheries for species with annual reproductive cycles (see e.g. [@mangel2006theoretical], Chap. 6).
